COG-ED Manuscript

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
fixed fig caption issue

```{r Fig2cSA and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity."}

>>>>

<!-- (ref:Fig2cSA-caption) Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity.-->
```{r Fig2cSA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity."}
